Contracts for unions and intersections are hard for Nickel

### 2021-06-07 paper.tex
Superficial pass on sections 4 & 5

\begin{figure}[h]
\begin{lstlisting}[language=nickel, title=Original]
let f | Num -> (Bool -> Num @| Bool -> Str)
      = fun x y => if y then x else "False"
in (f 1 true, f 1 false)
\end{lstlisting}
\begin{lstlisting}[language=nickel, title=Optimized]
let f | Num -> (Bool -> Num @| Bool -> MStr)
      = fun x y => if y then x else "False"
let g = f 1 in
(g true, g false)
\end{lstlisting}
\caption{Equivalent programs, with inlining or CSE applied}
\label{fig:optimized-programs}
\end{figure}

@@

In an higher-order intersection contract, blame is raised when:
\begin{description}
    \item[Negative blame] The argument fails \emph{both} components.
    \item[Positive blame] The function fails \emph{one} component that the
        argument previously satisfied.
\end{description}

@@

\begin{figure}[h]
\begin{lstlisting}[language=nickel]
let C = fun f => f 0 == 0 in
let g | (String -> String) @& C
      = fun x => x
\end{lstlisting}
\caption{Intersection and user defined contracts}
\label{fig:inter-flat-contracts}
\end{figure}

>>>>

\begin{figure}[h]
\begin{lstlisting}[language=nickel, title=Original]
let f | Num -> (Bool -> Num @| Bool -> Str)
      = fun x y => if y then x else "False"
in (f 1 true, f 1 false)
\end{lstlisting}
\begin{lstlisting}[language=nickel, title=Optimized]
let f | Num -> (Bool -> Num @| Bool -> Str)
      = fun x y => if y then x else "False"
let g = f 1 in
(g true, g false)
\end{lstlisting}
\caption{Equivalent programs, with inlining or CSE applied}
\label{fig:optimized-programs}
\end{figure}

@@

In an higher-order intersection contract, blame is raised when:
\begin{description}
    \item[Faulty caller] The argument fails \emph{both} components.
    \item[Faulty implementation] The function fails \emph{one} component that the
        argument previously satisfied.
\end{description}

@@

\begin{figure}[h]
\begin{lstlisting}[language=nickel]
let C = contracts.fromPred (fun f =>
  f 0 == 0) in
let g | (String -> String) @& C
      = fun x => x
\end{lstlisting}
\caption{Intersection and user defined contracts}
\label{fig:inter-flat-contracts}
\end{figure}
